### 2020-11-20 05_Thesis/THESIS_LaTeX/Appendices/Appendix_ViscosityCurves.tex
diameter fetching

\chapter{Critical Concentrations} % Main appendix title

\label{Appendix_CriticalConcentrations} % Change X to a consecutive letter; for referencing this appendix elsewhere, use \ref{AppendixX}

\begin{figure}[!th]
\centering
\includegraphics[width=\textwidth]{./Figures/c_vs_v_PEOinSU8.png}
\decoRule
\caption[Viscosity as a function of shear rate for Poly(Ethylene Oxide) (PEO) and SU-8 2002 solutions]{Viscosity as a function of shear rate for Poly(Ethylene Oxide) (PEO) and SU-8 2002 solutions}
\label{fig:c_vs_v_PEOinSU8}
\end{figure}

\begin{figure}[!th]
\centering
\includegraphics[width=\textwidth]{./Figures/c_vs_v_PSinTHF.png}
\decoRule
\caption[Viscosity as a function of shear rate for Polystyrene (PS) and Tetrahydrofuran (THF) solutions]{Viscosity as a function of shear rate for Polystyrene (PS) and Tetrahydrofuran (THF) solutions}
\label{fig:c_vs_v_PSinTHF}
\end{figure}

\begin{figure}[!th]
\centering
\includegraphics[width=\textwidth]{./Figures/c_vs_v_PSBinNMP.png}
\decoRule
\caption[Viscosity as a function of shear rate for Poly(Styrene-co-Butadiene) (PSB) and 1-Methyl-2-Pyrrolidinone (NMP) solutions]{Viscosity as a function of shear rate for Poly(Styrene-co-Butadiene) (PSB) and 1-Methyl-2-Pyrrolidinone (NMP)}
\label{fig:c_vs_v_PSBinNMP}
\end{figure}

\begin{figure}[!th]
\centering
\includegraphics[width=\textwidth]{./Figures/c_vs_v_PSBinTHF-DMF.png}
\decoRule
\caption[Viscosity as a function of shear rate for Poly(Styrene-co-Butadiene) (PSB), Tetrahydrofuran (THF) and N,N-Dimethylformamide (DMF) solutions]{Viscosity as a function of shear rate for Poly(Styrene-co-Butadiene) (PSB), Tetrahydrofuran (THF) and N,N-Dimethylformamide (DMF) solutions}
\label{fig:c_vs_v_PSBinTHF-DMF}
\end{figure}

\begin{figure}[!th]
\centering
\includegraphics[width=\textwidth]{./Figures/c_vs_v_PSMSinDMF.png}
\decoRule
\caption[Viscosity as a function of shear rate for Poly(Styrene-co-alpha-Methylstyrene) (PSMS) and N,N-Dimethylformamide (DMF) solutions]{Viscosity as a function of shear rate for Poly(Styrene-co-alpha-Methylstyrene) (PSMS) and N,N-Dimethylformamide (DMF) solutions}
\label{fig:c_vs_v_PSMSinDMF}
\end{figure}

\begin{figure}[!th]
\centering
\includegraphics[width=\textwidth]{./Figures/c_vs_v_PCKinCHL.png}
\decoRule
\caption[Viscosity as a function of shear rate for Poly(9-Vinylcarbazole) (PVK) and Chloroform (CHL) solutions]{Viscosity as a function of shear rate for Poly(9-Vinylcarbazole) (PVK) and Chloroform (CHL) solutions}
\label{fig:c_vs_v_PCKinCHL}
\end{figure}

\begin{figure}[!th]
\centering
\includegraphics[width=\textwidth]{./Figures/c_vs_v_PCKinSU8.png}
\decoRule
\caption[Viscosity as a function of shear rate for Poly(9-Vinylcarbazole) (PVK) and SU-8 2002 solutions]{Viscosity as a function of shear rate for Poly(9-Vinylcarbazole) (PVK) and SU-8 2002 solutions}
\label{fig:c_vs_v_PCKinSU8}
\end{figure}

>>>>

\chapter{Flow Curves} % Main appendix title

\label{AppendixX} % Change X to a consecutive letter; for referencing this appendix elsewhere, use \ref{AppendixX}

\begin{figure}[!th]
\centering
\includegraphics[width=\textwidth]{./Figures/plt_PEOwtinSU8.png}
\decoRule
\caption[Viscosity as a function of shear rate for Poly(Ethylene Oxide) (PEO) and SU-8 2002 solutions]{Viscosity as a function of shear rate for Poly(Ethylene Oxide) (PEO) and SU-8 2002 solutions}
\label{fig:plt_PEOwtinSU8}
\end{figure}

\begin{figure}[!th]
\centering
\includegraphics[width=\textwidth]{./Figures/plt_PSwtinTHF.png}
\decoRule
\caption[Viscosity as a function of shear rate for Polystyrene (PS) and Tetrahydrofuran (THF) solutions]{Viscosity as a function of shear rate for Polystyrene (PS) and Tetrahydrofuran (THF) solutions}
\label{fig:plt_PSwtinTHF}
\end{figure}

\begin{figure}[!th]
\centering
\includegraphics[width=\textwidth]{./Figures/plt_PSBwtinNMP.png}
\decoRule
\caption[Viscosity as a function of shear rate for Poly(Styrene-co-Butadiene) (PSB) and 1-Methyl-2-Pyrrolidinone (NMP) solutions]{Viscosity as a function of shear rate for Poly(Styrene-co-Butadiene) (PSB) and 1-Methyl-2-Pyrrolidinone (NMP)}
\label{fig:plt_PSBwtinNMP}
\end{figure}

\begin{figure}[!th]
\centering
\includegraphics[width=\textwidth]{./Figures/plt_PSBwtinTHFandDMF.png}
\decoRule
\caption[Viscosity as a function of shear rate for Poly(Styrene-co-Butadiene) (PSB), Tetrahydrofuran (THF) and N,N-Dimethylformamide (DMF) solutions]{Viscosity as a function of shear rate for Poly(Styrene-co-Butadiene) (PSB), Tetrahydrofuran (THF) and N,N-Dimethylformamide (DMF) solutions}
\label{fig:plt_PSBwtinTHFandDMF}
\end{figure}

\begin{figure}[!th]
\centering
\includegraphics[width=\textwidth]{./Figures/plt_PSMSwtinDMF.png}
\decoRule
\caption[Viscosity as a function of shear rate for Poly(Styrene-co-alpha-Methylstyrene) (PSMS) and N,N-Dimethylformamide (DMF) solutions]{Viscosity as a function of shear rate for Poly(Styrene-co-alpha-Methylstyrene) (PSMS) and N,N-Dimethylformamide (DMF) solutions}
\label{fig:plt_PSMSwtinDMF}
\end{figure}

\begin{figure}[!th]
\centering
\includegraphics[width=\textwidth]{./Figures/plt_PVKwtinCHL.png}
\decoRule
\caption[Viscosity as a function of shear rate for Poly(9-Vinylcarbazole) (PVK) and Chloroform (CHL) solutions]{Viscosity as a function of shear rate for Poly(9-Vinylcarbazole) (PVK) and Chloroform (CHL) solutions}
\label{fig:plt_PVKwtinCHL}
\end{figure}

\begin{figure}[!th]
\centering
\includegraphics[width=\textwidth]{./Figures/plt_PVKwtinSU8.png}
\decoRule
\caption[Viscosity as a function of shear rate for Poly(9-Vinylcarbazole) (PVK) and SU-8 2002 solutions]{Viscosity as a function of shear rate for Poly(9-Vinylcarbazole) (PVK) and SU-8 2002 solutions}
\label{fig:plt_PVKwtinSU8}
\end{figure}

### 2020-11-20 05_Thesis/THESIS_LaTeX/Chapters/3.tex
diameter fetching

%\begin{table}[!th]
%\centering
%\caption[Set of Polymer-Solvent Systems to be Analyzed]{Set of Polymer-Solvent Systems to be Analyzed}
%\begin{tabularx}{\textwidth}{ l >{\raggedright\arraybackslash}X }
%\hline
%\textbf{Polymer}                                & \textbf{Solvent}                                      \\
%\hline
%Poly(Ethylene Oxide) (PEO) + SU-8 2002 (SU-8)   & Cyclopentanone                                        \\
%Polystyrene (PS)                                & Tetrahydrofuran (THF)                                 \\
%Poly(Styrene-co-Butadiene) (PSB)                & 1-Methyl-2-Pyrrolidinone (NMP)                        \\
%Poly(Styrene-co-Butadiene) (PSB)                & Tetrahydrofuran (THF) and N,N-Dimethylformamide (DMF) \\
%Poly(Styrene-co-alpha-Methylstyrene) (PSMS)     & N,N-Dimethylformamide (DMF)                           \\
%Poly(9-Vinylcarbazole) (PVK)                    & Chloroform (CHL)                                      \\
%Poly(9-Vinylcarbazole) (PVK) + SU-8 2002 (SU-8) & Cyclopentanone                                        \\
%\hline
%\end{tabularx}
%\label{tab:candidatePolymerSolventSystems}
%\end{table}

@@

Seven polymer-solvent combinations are to be tested. The Poly(Ethylene Oxide) and SU-8 2002 combination is what has been used in past work \cite{Cardenas2017, Flores2017}, and will be used as the control sample set. The selected polymer-solvent combinations are to investigate the ability of oxygenless polymers to be electrospun and then carbonized into vitreous carbon. Tables \ref{tab:PEOinSU8}, \ref{tab:PSBinNMP}, \ref{tab:PSBinTHFnDMF}, \ref{tab:PSMSinDMF}, \ref{tab:PSinTHF}, \ref{tab:PVKinCHL}, and \ref{tab:PVKinSU8} list the prepared polymer systems. Tetrabutylammonium tetrafluoroborate (TBF) was added to all solutions to increase the conductivity of the solution. SU-8 contains $71\%$ of cyclopentanone, which acts as the solvent (Figure \ref{fig:su8Components}) \cite{Microchem2012}.

@@

As depicted in the rheological results in Figures \ref{}, the constant-viscosity (Newtonian-like) behavior before the shear thinning onset was captured. In all samples, a noticeable shear-thinning behavior is observed. The Carreau–Yasuda model \cite{RByron1987} was fitted to the cone-and-plate  measurements to compute the zero-shear viscosity of each sample.

\begin{figure}[!th]
\centering
\includegraphics[width=\textwidth]{./Figures/plt_FlowCurves_PEOinSU8.png}
\decoRule
\caption[Viscosity as a function of shear rate for Poly(Ethylene Oxide) (PEO) and SU-8 2002 solutions]{Viscosity as a function of shear rate for Poly(Ethylene Oxide) (PEO) and SU-8 2002 solutions}
\label{fig:plt_FlowCurves_PEOinSU8}
\end{figure}

>>>>

%\begin{table}[!th]
%\centering
%\caption[Set of Polymer-Solvent Systems to be Analyzed]{Set of Polymer-Solvent Systems to be Analyzed}
%\begin{tabularx}{\textwidth}{ l >{\raggedright\arraybackslash}X }
%\hline
%\textbf{Polymer}                                & \textbf{Solvent}                                      \\
%\hline
%Poly(Ethylene Oxide) (PEO) + SU-8 2002 (SU-8)   & Cyclopentanone                                        \\
%Polystyrene (PS)                                & Tetrahydrofuran (THF)                                 \\
%Poly(Styrene-co-Butadiene) (PSB)                & 1-Methyl-2-Pyrrolidinone (NMP)                        \\
%Poly(Styrene-co-Butadiene) (PSB)                & Tetrahydrofuran (THF) and N,N-Dimethylformamide (DMF) \\
%Poly(Styrene-co-alpha-Methylstyrene) (PSMS)     & N,N-Dimethylformamide (DMF)                           \\
%Poly(9-Vinylcarbazole) (PVK)                    & Chloroform (CHL)                                      \\
%Poly(9-Vinylcarbazole) (PVK) + SU-8 2002 (SU-8) & Cyclopentanone (CPO)                                  \\
%\hline
%\end{tabularx}
%\label{tab:candidatePolymerSolventSystems}
%\end{table}

@@

Seven polymer-solvent combinations are to be tested. The Poly(Ethylene Oxide) and SU-8 2002 combination is what has been used in past work \cite{Cardenas2017, Flores2017}, and will be used as the control sample set. The selected polymer-solvent combinations are to investigate the ability of oxygenless polymers to be electrospun and then carbonized into vitreous carbon. Tables \ref{tab:PEOinSU8}, \ref{tab:PSBinNMP}, \ref{tab:PSBinTHFnDMF}, \ref{tab:PSMSinDMF}, \ref{tab:PSinTHF}, \ref{tab:PVKinCHL}, and \ref{tab:PVKinSU8} list the prepared polymer systems. Tetrabutylammonium tetrafluoroborate (TBF) was added to all solutions to increase the conductivity of the solution. SU-8 contains $71\%$ of cyclopentanone (CPO), which acts as the solvent (Figure \ref{fig:su8Components}) \cite{Microchem2012}.

@@

As depicted in the rheological results in Figures \ref{fig:plt_PEOwtinSU8}, \ref{fig:plt_PSwtinTHF}, \ref{fig:plt_PSBwtinNMP}, \ref{fig:plt_PSBwtinTHFandDMF}, \ref{fig:plt_PSMSwtinDMF}, \ref{fig:plt_PVKwtinCHL} and \ref{fig:plt_PVKwtinSU8}, the constant-viscosity (Newtonian-like) behavior before the shear thinning onset was captured. In all samples, a noticeable shear-thinning behavior is observed with an increase in viscosity with concentration increments. The shear-thinning behavior can be interpreted as the alignment of polymer chains to the flow in the direction of the applied shear stress. \cite{Floreshernandez2020} The Carreau–Yasuda model (Equation \ref{eqn:carreauYasudaModel}) \cite{RByron1987} was fitted to the cone-and-plate  measurements to compute the zero-shear viscosity of each sample.

\begin{equation}\label{eqn:carreauYasudaModel}
    \eta = \frac{\eta_0 - \eta_{\infty}}{\left[1 + \left(\kappa \dot{\gamma}\right)^a\right]^{\frac{(1 - n)}{a}}} + \eta_{\infty}
\end{equation}

Where: $\eta$ is the viscosity, $\dot{\gamma}$ the shear rate, $\eta_{\infty}$ the  infinite shear rate viscosity, $\eta_0$ the zero shear rate viscosity, $\kappa$ is the time constant, $n$ the Power Law index, $a$ the width of the transition region between the zero shear viscosity and the Power Law region. The model was fitted to the rheologial data to estimate $\eta_0$. Then, $\eta_0$ values are used to create diagrams that describe the effect of polymer concentration on the solution viscosity, as described in Figure \ref{fig:concentrationViscosityPlotExplained}. The critical concentrations are calculated from the change in slope in the zero-shear viscosity to concentration relationship as depicted in Figure \ref{fig:criticalConcentrationCalculation} for the PEO in SU-8 solutions. Appendix \ref{Appendix_CriticalConcentrations} contains the diagrams of the other polymer-solvent systems.

\begin{figure}[!th]
\centering
\includegraphics[width=\textwidth]{./Figures/criticalConcentrationCalculation.png}
\decoRule
\caption[Estimation of the Critical Concentration of the PEO in SU-8 solutions]{The change in slope is given at 25 $wt\%$ PEO, which suggests that at 25 $wt\%$ the polymer chains are entangled.}
\label{fig:criticalConcentrationCalculation}
\end{figure}

\begin{table}[!th]
\centering
\caption[Calculated Critical/Spinnable Concentrations for each Polymer-Solvent System]{Calculated Critical/Spinnable Concentrations for each Polymer-Solvent System}
\begin{tabular}{lllll}
\hline
\textbf{Polymer} & \textbf{Molecular Weight $[\textrm{g} \cdot \textrm{mol}]$} & \textbf{Solvent} & \textbf{$c^* [\textrm{wt}\%]$} & \textbf{$\eta_0 [\textrm{Pa} \cdot \textrm{s}]$} \\
\hline
PEO  & 4,000,000                  & CPO (SU-8)  & 0.25  & 60.022 \\
PS   & 192,000                    & THF         & 20.00 & 0.166  \\
PSB  & 490,000   \cite{Doan2013}  & NMP         & 8.00  & 0.028  \\
PSB  & 490,000   \cite{Doan2013}  & THF and DMF & 15.00 & 0.092  \\
PSMS & 2,658,076 \cite{Colby1987} & DMF         & 5.00  & 0.282  \\
PVK  & 1,100,000                  & CHL         & 15.00 & 41.861 \\
PVK  & 1,100,000                  & CPO (SU-8)  & 0.75  & 49.657 \\
\hline
\end{tabular}
\label{tab:calculatedSpinnableConcentrations}
\end{table}

Table \ref{tab:calculatedSpinnableConcentrations} summarizes the calculated critical concentrations for each system. In general, the critical concentration $c^*$ has proportional relationship with the polymer molecular weight, as a polymer's molecular weight greatly influences the solution viscosity. First, the structure of the polymer chain has an effect on its solubility as the intermolecular interactions between long molecules are stronger and the solvent molecules take longer to diffuse within the polymer aggregates. \cite{Ramakrishna2005} Second, the viscosity of a polymer solution will be smaller when a polymer of low molecular weight is dissolved than a solution of the same polymer but of a higher molecular weight. \cite{Ramakrishna2005} The molecular weight of the polymer describes the length of the polymer chain, which has an effect on the viscosity of the solution. Since the polymer length defines the amount of entanglement of the polymer chains in the solvent, a lower molecular weight shall be compensated by higher concentrations to reach the desired viscosity.
